### 2018-04-05 Paper/sense.tex
..

\noindent Latin hypercube sampling in the 7D parameter space is used to estimate $\mu_i$. Note that $G$ must 
exhibit a smooth variation with each parameter so that the derivative in Eq.~\ref{eq:mu} can be estimated
with reasonable accuracy either analytically or numerically. 
 In this work, we examine the suitability of this
approach based on DGSM for the present application involving thermal transport in bulk Si. We define a 
normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:

@@

\noindent The choice of $\mathcal{C}_i$ is specific to the marginal probability distribution of the uncertain model
parameter, $\theta_i$. In this work, we consider all uncertain parameters to be uniformly
distributed in the interval~$[a,b]$ in which case $\mathcal{C}_i$  is given as $(b-a)^{2}/\pi^2$~\cite{Roustant:2014}.

>>>>

\noindent Latin hypercube sampling in the 7D parameter space is used to estimate $\mu_i$. Note that $G$ must 
exhibit a smooth variation with each parameter so that the derivative in Eq.~\ref{eq:mu} can be estimated
with reasonable accuracy either analytically or numerically. 
We define a normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:

@@

\noindent The choice of $\mathcal{C}_i$ is specific to the marginal probability distribution of the uncertain model
parameter, $\theta_i$. 
%We consider all uncertain parameters to be uniformly
%distributed in the interval~$[a,b]$ in which case $\mathcal{C}_i$  is given as $(b-a)^{2}/\pi^2$~\cite{Roustant:2014}.
The underlying methodology for implementing DGSM to the present application involving thermal transport in bulk Si,
and our key findings are presented in the following section.

\subsection{DGSM for SW potential parameters}
\label{sub:dgsm}

We aim to compute the derivate-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
Sobol total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
and $l$ being the upper and lower bounds of the interval respectively.

Performing NEMD simulations using perturbed values of the SW potential parameters could however be challenging.
For certain combinations of the SW potential parameter values, the steady-state thermal
energy exchange between the thermostats is found to be non-physical at the end of the simulation. We believe that
this happened in situations where the structure had deviated too far from the equilibrium state and hence the
structural integrity of the bar is lost as illustrated in Figure~\ref{fig:dgsm1}(a). To avoid this
issue, we added an NPT ensemble prior to NVT in the NEMD simulation as shown in the following diagram:

\begin{center}

NPT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVE \hspace{5mm}
$\rightarrow$ \hspace{5mm} NVE
\\ \vspace{1mm}
\tiny [Relax the system]~[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

\tiny{N: Number of Atoms~~~P: Pressure~~~V: Volume~~~T: Temperature~~~E: Energy}
\end{center}

\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).

### 2018-04-05 Paper/setup.tex
..

Non-equilibrium molecular dynamics (NEMD) simulations are performed in LAMMPS~\cite{Plimpton:2007}
by applying a thermal gradient by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$. 
The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}. The set of
inputs to LAMMPS is provided below in Table~1. Note that specific values for the length of the bar
and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
minimizing temperature fluctuations during different stages of the simulation was performed to optimize for the
choice of height and width of the bar as well as the duration of the simulation.

@@

NVT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVE \hspace{5mm}
$\rightarrow$ \hspace{5mm} NVE
\\ \vspace{1mm}
\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

>>>>

Non-equilibrium molecular dynamics (NEMD) simulations are performed in LAMMPS~\cite{Plimpton:2007}
by applying a thermal gradient by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$. 
The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}. The set of
inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar
and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
minimizing temperature fluctuations during different stages of the simulation was performed to optimize for the
choice of height and width of the bar as well as the duration of the simulation.

@@

NVT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVE \hspace{5mm}
$\rightarrow$ \hspace{5mm} NVE
\\ \vspace{1mm}
\tiny \hspace{-5mm}[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}
